Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

	Now we bound $\TAlg(\sigma_I)$ by summing the intra-component counters of each cluster at the end of the phase.
	The sum of intra-component counters in a cluster of type $C_3$ is at most $3 \alpha - 1$: two pairs of nodes from the component are saturated and its counter is $\alpha$ each, and the counter of the third, unsaturated pair is at most $\alpha-1$.
	The sum of counters inside $C_1$ is $0$, and inside $C_2$ it is $\alpha$.
	Summing over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

@@

	Moreover, \TAlg paid for all requests from $\sigma_E$, and thus $\TAlg(\sigma_E) = |\sigma_E|$.
	In total, the cost of \TAlg is at most $\TAlg(\sigma_I) + \TAlg(\sigma_E) + \TAlg(M) \leq 11\alpha\cdot \ell + |\sigma_E|$ during this phase.

@@

	%First, we estimate the cost related to $\sigma_I$.
	We have $\OPT(M) + \OPT(\sigma_I) \geq \alpha$, as the phase ended when the components of \TAlg{} could not be partitioned without splitting them.
	Hence, for every possible partition of $\OPT$, there exists a~non-collocated pair of nodes with at least $\alpha$ requests between them, and
	$\OPT$ either served them remotely or performed a~migration.

	\medskip
	Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to requests $\sigma_E$.
	Fix a~partition for \OPT prior serving the sequence $\sigma_E$.
	Even without migrations, \OPT may mitigate paying for requests between at most $3\ell$ pairs of nodes that can be collocated in its clusters.
	Recall that $\sigma_E$ consists of requests to unsaturated pairs, and it accounts only for requests that increased the counter (i.e., external requests), and the counter of an unsaturated pair is at most $\alpha - 1$.
	Hence, $\OPT$ may mitigate at most $3\ell\cdot(\alpha - 1)$ requests from $\sigma_E$.
	Finally, during the phase, \OPT is faced with at least $\chi := |\sigma_E| - 3\ell\cdot(\alpha-1)$ requests from $\sigma_E$ that it cannot mitigate.

>>>>

	We bound $\TAlg(\sigma_I)$ by summing the intra-component counters of each cluster at the end of the phase.
	The sum of intra-component counters in a cluster of type $C_3$ is at most $3 \alpha - 1$: two pairs of nodes from the component are saturated and its counter is $\alpha$ each, and the counter of the third, unsaturated pair is at most $\alpha-1$.
	The sum of counters inside $C_1$ is~$0$, and inside $C_2$ it is $\alpha$.
	Summing over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 3\alpha\cdot\ell$.

@@

	Furthermore, \TAlg paid for all requests from $\sigma_E$, and thus $\TAlg(\sigma_E) = |\sigma_E|$.
	In total, the cost of \TAlg is at most $\TAlg(\sigma_I) + \TAlg(\sigma_E) + \TAlg(M) \leq 11\alpha\cdot \ell + |\sigma_E|$ during this phase.

@@

	First, we show $\OPT(M) + \OPT(\sigma_I) \geq \alpha$.
	Assume that \OPT's partition is fixed throughout the phase (as otherwise \OPT pays $\alpha$ for a migration).
	The phase ended when the components of \TAlg{} could not be partitioned without splitting them.
	Hence, for every possible partition of $\OPT$, there exists a~non-collocated saturated pair, and
	$\OPT$ paid for $\alpha$ requests that saturated the pair.

	Next, we relate the costs of $\TAlg$ and $\OPT$ with respect to requests $\sigma_E$.
	Fix a~partition for \OPT prior serving the sequence $\sigma_E$.
	Even without migrations, \OPT may mitigate paying for requests between at most $3\ell$ pairs of nodes that can be collocated in its clusters.
	Recall that $\sigma_E$ consists of requests to unsaturated pairs, and it accounts only for requests that increased the counter (i.e., external requests), and the counter of an unsaturated pair is at most $\alpha - 1$.
	Hence, $\OPT$ may mitigate at most $3\ell\cdot(\alpha - 1)$ requests from $\sigma_E$.
	Finally, during the phase, \OPT is faced with at least $\chi := |\sigma_E| - 3\ell\cdot(\alpha-1)$ requests from $\sigma_E$ that it cannot mitigate.
